Second-Generation Web Interface to Correcting ASR Output

### 2018-05-21 2018-ftc-vancouver/webapp.tex
more reviewer feedback adaptations

\begin{filecontents}{citace.bib}
@inproceedings{kruuza2012making,
  title={Making Community and ASR Join Forces in Web Environment},
  author={Kr\r{u}za, Old{\v{r}}ich and Peterek, Nino},
  booktitle={International Conference on Text, Speech and Dialogue},
  pages={415--421},
  year={2012},
  organization={Springer}
}
@article{codd1970relational,
  title={A relational model of data for large shared data banks},
  author={Codd, Edgar F},
  journal={Communications of the ACM},
  volume={13},
  number={6},
  pages={377--387},
  year={1970},
  publisher={ACM}
}
@article{adenot2013web,
  title={Web audio api},
  author={Adenot, Paul and Wilson, Chris and Rogers, Chris},
  journal={W3C, October},
  volume={10},
  year={2013}
}
@article{abramov2015redux,
  title={Redux},
  author={Abramov, D},
  journal={React Community, c},
  year={2015}
}
@article{hajek2007cesky,
  title={\v{C}esk\'{y} mystik Karel Mako\v{n}},
  author={Jurik H\'{a}jek},
  journal={Dingir},
  year={2007},
  volume={2007/4},
  pages={142--143},
  publisher={Dingir, s.r.o.},
  ISSN={1212-1371},
  editor={Zden\v{e}k Vojt\'{i}\v{s}ek}
}
@inproceedings{ide2010manually,
  title={The manually annotated sub-corpus: A community resource for and by the people},
  author={Ide, Nancy and Fellbaum, Christiane and Baker, Collin and Passonneau, Rebecca},
  booktitle={Proceedings of the ACL 2010 conference short papers},
  pages={68--73},
  year={2010},
  organization={Association for Computational Linguistics}
}
@article{bojar2008czeng,
  title={CzEng 0.7: Parallel Corpus with Community-Supplied Translations},
  author={Bojar, Ond{\v{r}}ej and Jan{\'\i}{\v{c}}ek, Miroslav and {\v{C}}e{\v{s}}ka, Pavel and Be{\v{n}}a, Peter and others},
  journal={LREC 2008},
  year={2008}
}
@inproceedings{5494979,
  author={M. Marge and S. Banerjee and A. I. Rudnicky},
  booktitle={2010 IEEE International Conference on Acoustics, Speech and Signal Processing},
  title={Using the Amazon Mechanical Turk for transcription of spoken language},
  year={2010},
  volume={},
  number={},
  pages={5270-5273},
  keywords={linguistics;natural language processing;speech processing;Amazon mechanical turk service;MTurk marketplace;Rover voting scheme;speaker demographics;spoken language transcription;transcription guideline;Computer science;Costs;Demography;Gold;Guidelines;Humans;Natural languages;Recruitment;Speech synthesis;Streaming media;crowd sourcing;speech transcription},
  doi={10.1109/ICASSP.2010.5494979},
  ISSN={1520-6149},
  month={March},
}
@article{reese2010wikicorpus,
  title={Wikicorpus: A word-sense disambiguated multilingual wikipedia corpus},
  author={Reese, Samuel and Boleda, Gemma and Cuadros, Montse and Rigau, German},
  year={2010},
  publisher={Citeseer}
}
\end{filecontents}

@@

Basically the meat of his teachings is systematically encompassed in his written
works, whilst the talks contain the sauce: talks tailored to the audience,
answers to questions, personal experiences, behind-the-scenes to the books etc.

@@

Our project is not the first community-driven corpus annotation. We can mention
the Manually annotated sub-corpus\cite{ide2010manually}, where annotations of
various kinds are gathered from volunteers, or the
Wikicorpus\cite{reese2010wikicorpus}, a corpus of Wikipedia articles with some
linguistic annotation. Our project may reach profound similarities with these in
the future, when we no longer focus on the transcription itself but rather on
annotation. There is also CzEng\cite{bojar2008czeng}, the Czech-English Parallel
Corpus, where a large part of the translation is provided by volunteers. The
similarity in setting is considerable as both projects involve a
machine-produced erroneous derivative of the original material (in our case
audio transcriptions, in the case of CzEng Czech translations of English texts),
and a community of volunteers corrects these. But the specifics of the projects
bring different challenges and dictate different approaches. Finally, Marge
2009\cite{5494979} investigates using The Mechanical Turk to obtain audio
transcriptions.

@@

@@

We have pointed out the differences in our setting to others. Now we shall
describe how we implemented the program.

@@

With our web application, a user can listen to recorded speech, see its
transcription with the currently played word highlighted, commit corrections to
the transcription, and inspect a word as well as a span of text and audio. The
corrections are checked by a forced-alignment mechanism on the server side. Our
solution overcomes performance challenges and is a serious improvement from the
original version. More widespread usage as well as employing it on another data
set is to be done.

>>>>

\begin{filecontents}{citace.bib}
@inproceedings{kruuza2012making,
  title={Making Community and ASR Join Forces in Web Environment},
  author={Kr\r{u}za, Old{\v{r}}ich and Peterek, Nino},
  booktitle={International Conference on Text, Speech and Dialogue},
  pages={415--421},
  year={2012},
  organization={Springer}
}
@article{codd1970relational,
  title={A relational model of data for large shared data banks},
  author={Codd, Edgar F},
  journal={Communications of the ACM},
  volume={13},
  number={6},
  pages={377--387},
  year={1970},
  publisher={ACM}
}
@article{adenot2013web,
  title={Web audio api},
  author={Adenot, Paul and Wilson, Chris and Rogers, Chris},
  journal={W3C, October},
  volume={10},
  year={2013}
}
@article{mihalcea2004building,
  title={Building sense tagged corpora with volunteer contributions over the web},
  author={Mihalcea, Rada and Chklovski, Timothy},
  journal={Recent Advances in Natural Language Processing III: Selected Papers from RANLP 2003},
  volume={260},
  pages={357},
  year={2004},
  publisher={John Benjamins Publishing}
}
@article{abramov2015redux,
  title={Redux},
  author={Abramov, D},
  journal={React Community, c},
  year={2015}
}
@article{hajek2007cesky,
  title={\v{C}esk\'{y} mystik Karel Mako\v{n}},
  author={Jurik H\'{a}jek},
  journal={Dingir},
  year={2007},
  volume={2007/4},
  pages={142--143},
  publisher={Dingir, s.r.o.},
  ISSN={1212-1371},
  editor={Zden\v{e}k Vojt\'{i}\v{s}ek}
}
@inproceedings{ide2010manually,
  title={The manually annotated sub-corpus: A community resource for and by the people},
  author={Ide, Nancy and Fellbaum, Christiane and Baker, Collin and Passonneau, Rebecca},
  booktitle={Proceedings of the ACL 2010 conference short papers},
  pages={68--73},
  year={2010},
  organization={Association for Computational Linguistics}
}
@article{bojar2008czeng,
  title={CzEng 0.7: Parallel Corpus with Community-Supplied Translations},
  author={Bojar, Ond{\v{r}}ej and Jan{\'\i}{\v{c}}ek, Miroslav and {\v{C}}e{\v{s}}ka, Pavel and Be{\v{n}}a, Peter and others},
  journal={LREC 2008},
  year={2008}
}
@inproceedings{5494979,
  author={M. Marge and S. Banerjee and A. I. Rudnicky},
  booktitle={2010 IEEE International Conference on Acoustics, Speech and Signal Processing},
  title={Using the Amazon Mechanical Turk for transcription of spoken language},
  year={2010},
  volume={},
  number={},
  pages={5270-5273},
  keywords={linguistics;natural language processing;speech processing;Amazon mechanical turk service;MTurk marketplace;Rover voting scheme;speaker demographics;spoken language transcription;transcription guideline;Computer science;Costs;Demography;Gold;Guidelines;Humans;Natural languages;Recruitment;Speech synthesis;Streaming media;crowd sourcing;speech transcription},
  doi={10.1109/ICASSP.2010.5494979},
  ISSN={1520-6149},
  month={March},
}
@article{reese2010wikicorpus,
  title={Wikicorpus: A word-sense disambiguated multilingual wikipedia corpus},
  author={Reese, Samuel and Boleda, Gemma and Cuadros, Montse and Rigau, German},
  year={2010},
  publisher={Citeseer}
}
\end{filecontents}

@@

Mako\v{n}'s written works present his teachings in a systematic, comprehensible
fashion, while the recordings offer bonuses: talks tailored to the audience,
answers to questions, personal experiences, behind-the-scenes to the books etc.
The archive is freely accessible under the CC-BY license.

@@

@@

Our project is not the first involving community-driven corpus annotation. We
can mention the Manually annotated sub-corpus\cite{ide2010manually}, where
annotations of various kinds are gathered from volunteers, or the
Wikicorpus\cite{reese2010wikicorpus}, a corpus of Wikipedia articles with some
linguistic annotation. Our project may reach profound similarities with these in
the future, when we no longer focus on the transcription itself but rather on
annotation. There is also CzEng\cite{bojar2008czeng}, the Czech-English Parallel
Corpus, where a large part of the translation is provided by volunteers. The
similarity in setting is considerable as both projects involve a
machine-produced erroneous derivative of the original material (in our case
audio transcriptions, in the case of CzEng Czech translations of English texts),
and a community of volunteers correct these. But the specifics of the projects
bring different challenges and dictate different approaches. Marge
(2009)\cite{5494979} investigates using The Mechanical Turk to obtain audio
transcriptions. Mihalcea (2004)\cite{mihalcea2004building} offers a web
interface for word-sense disambiguation but focuses mostly on annotator conflict
resolution.

@@

\subsection{Usage}

We have no special assumption of the user beyond basic computer usage skills and
understanding the audio. We assume no prior training. There is a manual for
clearing common points of confusion. The main message in it is that anything
that is to be transcribed, should be should be transcribed with respect to
phonetic precision, even if it results in nonsensical character strings.

Anything except words spoken by the one speaker of interest is to be left
untranscribed, including noise or speech by other persons\footnote{We may later
add a speaker annotation}. Incomprehensible words are to be left uncorrected
(the ASR output kept) if the phones are unclear. If the phones uttered are clear
but it is not clear what word was meant, the word may be transcribed
phonetically.

A submitted transcribed segment always overwrites the present version but we
keep all the submissions in a database, so undo operations, clustering
submissions by their author etc. are possible but we had little need for this so
far.

\subsection{Implementation}

@@

With our web application, a user can listen to recorded speech, see its
transcription with the currently played word highlighted, commit corrections to
the transcription, and inspect a word. The corrections are checked by a
forced-alignment mechanism on the server side. Our solution overcomes
performance challenges and is a serious improvement from the original version.
All our codebase is open-source, accessible on
Github\footnote{https://github.com/sixtease/MakonReact} and we are actively
looking for similar datasets with communities to employ the application on.
